Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Added intro texts to Discussion and BG Tech chapters

In this project assignment, we integrate the fourteen \ac{SHA}-3 candidates in
the Tahoe-\ac{LAFS} and measure the performance impact. To be able to do this,
we create Python bindings for the best suited C implementations of the SHA-3
candidates, and alter the hash function calls in the source code of Tahoe.

@@

@@

\subsection{Theoretical optimized results}
These results are calculated using the best \ac{SUPERCOP} results for each
candidate from section \ref{sec:results:supercop}, the exact sizes for each
call to the hash function from section \ref{sec:results:tahoedata}, and
interpolation to estimate the time to hash a length not recorded by
\ac{SUPERCOP}. For lengths above 4096 the results for long data lanegths are
used. The results also assume only one core of the reference processor is used.

@@

% TODO: Intro

>>>>

In this project assignment, we integrate the 14 \ac{SHA}-3 candidates in
the Tahoe-\ac{LAFS} and measure the performance impact. To be able to do this,
we create Python bindings for the best suited C implementations of the SHA-3
candidates, and alter the hash function calls in the source code of Tahoe.

@@

This chapter provides background knowledge for the most important software and
technologies used in this project assignment, comprising of cryptographic hash
functions (in light of the \ac{NIST} competition), the \ac{SUPERCOP} toolkit,
Tahoe-\ac{LAFS}, and lastly Python and Cython.

@@

\subsection{Theoretical optimized results}

Tables \ref{tbl:tahoe:optimized_g} and \ref{tbl:tahoe:optimized_p} exhibit
the results calculated using the best \ac{SUPERCOP} implementation for each
candidate from Section \ref{sec:results:supercop}, the exact sizes for each
call to the hash function from Section \ref{sec:results:tahoedata}, and
interpolation to estimate the time to hash a length not recorded by
\ac{SUPERCOP}. For lengths above 4096B, the numbers for long data lengths are
used. The results also assume only one core of the reference processor is used.

@@

This chapter will provide comments on the results made, what the numbers
mean and why there are some inconsistencies. In addition, general
thoughts on the testing procedure and the \ac{SUPERCOP} toolkit will be
presented.
